---
title: "Generalized Extreme Value (GEV) Distribution"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    css: www/style.css
    navbar:
        - { icon: "fa-github", href: "https://github.com/Reckziegel/GEVSimulation", align: right }
        - { icon: "fa-linkedin", href: "https://www.linkedin.com/in/bernardoreckziegel/", align: right }
        - { icon: "fa-at", href: "mailto:bernardo_cse@hotmail.com", align: right }
    theme: 
      bootswatch: yeti
      version: 4
      bg: "#063853"
      fg: "#011A27"
      primary: "#E6DF34"
      base_font: 
        google: Ovo
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)
```

## Input {.sidebar}

```{r}
shiny::br()

shiny::sliderInput(
  inputId = "n_input", 
  label   = "Simulations", 
  min     = 1, 
  max     = 5000, 
  value   = 1000, 
  step    = 1)

shiny::sliderInput(
  inputId = "mean_input", 
  label   = "Mu", 
  min     = -0.20,
  max     = 0.20, 
  value   = 0, 
  step    = 0.001)

shiny::sliderInput(
  inputId = "sigma_input", 
  label   = "Sigma", 
  min     = 0.01, 
  max     = 0.5, 
  value   = 0.25,  
  step    = 0.01)

shiny::sliderInput(
  inputId = "shape_input", 
  label   = "Shape", 
  min     = -0.5, 
  max     = 0.5, 
  value   = 0, 
  step    = 0.01
)
```

```{r}
# Data Manipulation
gev_rand_rct <- shiny::reactive({
  fExtremes::rgev(n    = input$n_input, 
                  xi   = input$shape_input, 
                  mu   = input$mean_input, 
                  beta = input$sigma_input) 
})

gev_rand_sorted_rct <- shiny::reactive({
  sort(gev_rand_rct())
})

gev_rand_dens_rct <- shiny::reactive({
  fExtremes::dgev(x    = gev_rand_sorted_rct(), 
                  xi   = input$shape_input, 
                  mu   = input$mean_input, 
                  beta = input$sigma_input)
})

gev_rand_cdf_rct <- shiny::reactive({
  fExtremes::pgev(q    = gev_rand_sorted_rct(), 
                  xi   = input$shape_input, 
                  mu   = input$mean_input, 
                  beta = input$sigma_input)
})

highcharter_density <- shiny::reactive({
  data.frame(x = gev_rand_sorted_rct(), 
             d = 100 * (gev_rand_dens_rct() / sum(gev_rand_dens_rct())), 
             f = gev_rand_cdf_rct()
             )
})

# dist_type <- function(x) {
#   if (x < 0) {
#     paste0("Fréchet Distribution")
#   } else if (x == 0) {
#     paste0("Gumbel Distribution") 
#   } else {
#     paste0("Weibull Distribution")
#   }
# }



```

## Column {data-width="650"}

```{r}
highcharter::renderHighchart({
  highcharter::hchart(object = highcharter_density(),
                      type = "spline",
                      highcharter::hcaes(x = x, y = d)) |>
    highcharter::hc_xAxis(title = FALSE) |>
    highcharter::hc_yAxis(title = FALSE) |>
    highcharter::hc_title(text = "Probability Density Function (PDF)") |> 
    highcharter::hc_add_theme(highcharter::hc_theme_flatdark())
})
```

```{r}
highcharter::renderHighchart({
  highcharter::hchart(object = highcharter_density(),
                      type = "spline",
                      highcharter::hcaes(x = x, y = f)) |>
    highcharter::hc_xAxis(title = FALSE) |>
    highcharter::hc_yAxis(title = FALSE) |>
    highcharter::hc_title(text = "Cumulative Density Function (CDF)") |> 
    highcharter::hc_add_theme(highcharter::hc_theme_flatdark()) 
})
```

## Column {data-width="350"}

### Explanation

This app is designed to show the impact of that the parameters $\mu$, $\sigma$ and $\xi$ in the Generalized Extreme Value distribution (GEV).

The key parameter is $\xi$, that can encompass three types of limiting cases:

-   For $\xi = 0$, the _Gumbel_ distribution;

-   For $\xi > 0$, the _Weibull_ distribution; and

-   for $\xi < 0$: the _Fréchet_ distribution

Look how $\xi$ distorts the PDF to the right under Weibull parametrization. The
opposite happens with the Fréchet family (and a long left-tail arises).






